SCP Briefing Plots - Combined Intervention

### 2024-11-21 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Updated summary and vis scripts to the latest version (with fixed num priority subgroup plot and plots for individual priority subgroups and lone adult households)

@@

Results disaggregated by if household belongs to 0, 1, 2, 3+ priority subgroups.

>>>>

```{r "priority_subgroups", include=FALSE}
priority_subgroup_plot <- function(priority_group, scen) {

  priority_group <- paste0('priority_', priority_group)
  scen <- paste0(scen, '_together')

  #print(priority_group)
  #print(scen)

  data <- do.call(rbind, generate_df_list(priority_group, scen))

  #return(data)

  plot_data <- data %>%
    select(run_id, SF_12, mean_cost, year, scenario) %>%
    pivot_wider(names_from = scenario,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
                 names_to = c(".value", "scen"), 
                 names_sep = "\\.") %>%
    filter(scen != 'baseline')

  #return(plot_data)

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = priority_group) +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal()

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = priority_group) +
    xlab('Year') +
    ylab('Change in Mean SF-12 MCS') +
    theme_minimal()

  #print(p1)
  print(p2)
  #print(p3)

  # ggsave(filename = paste0(priority_group, '_smooth', '.png'),
  #        plot = p1)
  # 
  # ggsave(filename = paste0(priority_group, '_confint', '.png'),
  #        plot = p2)
}

# test <- priority_subgroup_plot(priority_group = 'child_under_one',
#                                scen = 'ChildPovertyReduction')
```

```{r}
priority_subgroup_plot(priority_group = 'child_under_one',
                               scen = 'ChildPovertyReduction')
priority_subgroup_plot(priority_group = 'ethnicity',
                               scen = 'ChildPovertyReduction')
priority_subgroup_plot(priority_group = 'mother_under_25',
                               scen = 'ChildPovertyReduction')
priority_subgroup_plot(priority_group = 'three_plus_children',
                               scen = 'ChildPovertyReduction')
```

@@

Results disaggregated by if household belongs to 0, 1, 2+ priority subgroups.
